---
title: "Ozone and ozone hole"
author: "Mirna van Hoek"
date: "12/27/2017"
output: ioslides_presentation
logo: ozoneholePlot.jpg
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Ozone

* is a colorless gas 
* in the troposphere it causes smog
* in the stratosphere it protects us from radiation.
* amount is measured in Dobson Units (DU)

## Ozone hole

* occurs during Southern Hemisphere spring
* is caused by chemical reactions with chlorine and bromine
* amount of ozone < 220 DU

There are two ways to measure ozone hole size:

* The amount of ozone (DU)
* The area covered by the ozone hole (km^2)


## Ozone hole size (DU)

```{r libs, warning=FALSE, error=FALSE, message=FALSE}
library(dplyr)
library(plotly)
```

```{r read ozone and temperature data, warning=FALSE, message=FALSE}
ozoneFile <- "/Users/mirna/Cousera/Data_Science/datasciencecoursera/ShinyTests/ozonholeData/ozonholeSize.csv"
ozoneMinFile <- "/Users/mirna/Cousera/Data_Science/datasciencecoursera/ShinyTests/ozonholeData/ozonMinimum.csv"
minStratTempFile <- "/Users/mirna/Cousera/Data_Science/datasciencecoursera/ShinyTests/ozonholeData/minStratTemp.csv"
ozoneSizeDF <- read.csv2(ozoneFile, sep="", dec=".", skip = 5, stringsAsFactors = FALSE)
ozoneMinDF <- read.csv2(ozoneMinFile, sep="", dec=".", skip = 5, stringsAsFactors = FALSE)
minStratTempDF <- read.csv2(minStratTempFile, sep="", dec=".", skip=6, stringsAsFactors = FALSE)
ozoneSizeDF <- ozoneSizeDF %>% select(Date, ozoneSize=Data) %>% mutate(Date=as.Date(Date))
ozoneMinDF <- ozoneMinDF %>% select(Date, ozoneMin=Data) %>% mutate(Date=as.Date(Date))
minStratTempDF <- minStratTempDF %>% select(Date, minStratTemp=Data) %>% mutate(Date=as.Date(Date))
combiDF <- inner_join(ozoneSizeDF, ozoneMinDF, by = "Date") %>% inner_join(., minStratTempDF, by = "Date")
filteredDF <- filter(combiDF, Date>=as.Date("2017-01-01"), ozoneSize>=0)
```


```{r plot OzoneMin, warning=FALSE, error=FALSE}
f <- list(
  family = "Courier New, monospace",
  size = 18,
  color = "#7f7f7f")

plot_ly( x=filteredDF$Date, y=filteredDF$ozoneMin, type="scatter", mode="markers", color =filteredDF$minStratTemp, marker=list(colorbar = list(title="Minimum Stratospheric Temperature (K)", titleside="right"))) %>% layout(xaxis=list(title="time", titlefont=f, range=c('2017-01-01', '2017-12-31')), yaxis=list(title="Ozone amount (DU)", titlefont=f))
```

## Ozone hole size (km^2)

```{r plot ozoneSize, warning=FALSE, error=FALSE}

plot_ly( x=filteredDF$Date, y=filteredDF$ozoneSize, type="scatter", mode="markers", color =filteredDF$minStratTemp, marker=list(colorbar = list(title="Minimum Stratospheric Temperature (K)", titleside="right"))) %>% layout(xaxis=list(title="time", titlefont=f, range=c('2017-01-01', '2017-12-31')), yaxis=list(text="Ozone hole area (km^2)", titlefont=f))
```

## Conclusion

The minimum amount of ozone and the maximum area covered by the ozone hole are not reached on the same day.

**Reference** 

_Source: [NASA Ozone Watch](https://ozonewatch.gsfc.nasa.gov)_



