---
title: "explanation"
output: html_document
---

## The aim

Please fill in the properties of the glass that you recovered from the crime scene and find out what most likely the type of glass is that you found.<br>
Good luck!

## Background

### Dataset

The guys from the lab have created a DB containing properties and type of pieces of glass found at crime scenes (dataset fgl in MASS package).


**Glass properties**
<br>

* Refractive Index (RI) (1.518xxxx)
* Percenages by weight of oxides
  * Sodium (Na)
  * Magnese (Mg)
  * Aluminium (Al)
  * Silicon (Si)
  * Potasium (K)
  * Calcium (Ca)
  * Barium (Ba)
  * Iron (Fe)


**Glass types**
<br>

  * window float glass (WinF)
  * window non-float glass (WinNF)
  * vehicle window glass (Veh)
  * containers (Con)
  * tableware (Tabl)
  * vehicle headlamps (Head)
  

  
**References**
<br><br>
Venables, W. N. and Ripley, B. D. (2002) Modern Applied Statistics with S. Fourth edition. Springer.

### Prediction
<br>

 * Model: Random forest
 
 ```{r model, eval=FALSE}
  fitControl <- trainControl(method = "cv", number = 5)
  fitRF <- train(type ~ ., data = fgl,
                 method = "rf",
                 trControl = fitControl)
```

 * new data: input from sliders
 * prediction given as probabilities
 
```{r prediction, eval=FALSE}
predict(trainedModel,
        newdata = inputs,
        type = "prob",
        predict.all = TRUE)
```


